%%comandos nuevos
\newcommand{\firmante}{1}
\newcommand{\thedate}{ 22 de mayo de 2025}
\newcommand{\memorando}{EPN-DOCDCTA-2025-0055-M}
\newcommand{\docente}{PhD. Roque Antonio Santos Torres}
\newcommand{\masculino}{1}
\newcommand{\departamento}{Departamento de Ciencias Nucleares}
\newcommand{\cargo}{Profesor Agregado a Tiempo Completo }
\newcommand{\onlyScopus}{0} % 1 Only Scopus, 0 All
\newcommand{\onlyEpnScopusAffil}{0} % 1 Only EPN
\newcommand{\onlyEpnRegionalAffil}{1} % 1 Only EPN
\newcommand{\onlyEpnMemoriasAffil}{1} % 1 Only EPN
\newcommand{\onlyEpnCapsAffil}{1} % 1 Only EPN
\newcommand{\doi}[3][gray]{\href{#2}{\color{#1}{#3}}}

%%SCOPUS
\newcommand{\numpublicacionesscopus}{10 }
%% 6 Artículos, 4 Artículos de Conferencia, 2 Capitulos de Libros y 1 Review
\newcommand{\distribucionArticulosScopus}{9 Artículos y 1 Articulo de Conferencia}
\newcommand{\areasTematicasITEM}
{
\item Physics and Astronomy
\item Engineering
\item Chemistry
\item Environmental Science
\item Earth and Planetary Sciences
\item Energy
\item Materials Science
\item Mathematics
\item Multidisciplinary








}
\newcommand{\numAreasTematicas}{9 }

\newcommand{\detalleScopus}
{
 
\item (2023) "e-RPT: Ecuadorian radioactive particle tracking. Proposal and evaluation of a low-budget RPT system with GEANT4". Applied Radiation and Isotopes. \textbf{Indexada en SCOPUS - Radiation (Q3)}.\doi{https://doi.org/10.1016/j.apradiso.2023.110754}{ DOI: 10.1016/j.apradiso.2023.110754}
\item (2023) "SAS GEANT4 application and machine learning algorithms for radioactive particle tracking". Radiation Physics and Chemistry. \textbf{Indexada en SCOPUS - Radiation (Q2)}.\doi{https://doi.org/10.1016/j.radphyschem.2023.111056}{ DOI: 10.1016/j.radphyschem.2023.111056}
\item (2022) "Simulation of a HPGe Detector with GEANT4". Revista Politecnica. \textbf{Indexada en SCOPUS - Applied Mathematics (Q4); Chemistry (miscellaneous) (Q4); Engineering (miscellaneous) (Q4); Environmental Engineering (Q4); Geochemistry and Petrology (Q4); Geotechnical Engineering and Engineering Geology (Q4); Physics and Astronomy (miscellaneous) (Q4)}.\doi{https://doi.org/10.33333/rp.vol50n2.01}{ DOI: 10.33333/rp.vol50n2.01}
\item (2021) "Ionizing radiation as adjuvant for the abiotic degradation of plastic bags containing pro-oxidant additives". Journal of Applied Polymer Science. \textbf{Indexada en SCOPUS - Chemistry (miscellaneous) (Q2); Materials Chemistry (Q2); Polymers and Plastics (Q2); Surfaces, Coatings and Films (Q2)}.\doi{https://doi.org/10.1002/app.49664}{ DOI: 10.1002/app.49664}
\item (2020) "Viscosity Study in a Crude Oil Additive with Dispersants and Asphaltene Solvent". Revista Politecnica. \textbf{Indexada en SCOPUS - Applied Mathematics; Chemistry (miscellaneous); Engineering (miscellaneous); Environmental Engineering; Geochemistry and Petrology; Geotechnical Engineering and Engineering Geology; Physics and Astronomy (miscellaneous)}.\doi{https://doi.org/10.33333/rp.vol46n2.01}{ DOI: 10.33333/rp.vol46n2.01}
\item \textbf{(2018) "Simulated time-dependent data to estimate uncertainty in fluid flow measurements". Nuclear Engineering and Design. Indexada en SCOPUS - Materials Science (miscellaneous) (Q1); Mechanical Engineering (Q1); Nuclear and High Energy Physics (Q1); Nuclear Energy and Engineering (Q1); Safety, Risk, Reliability and Quality (Q1); Waste Management and Disposal (Q1)}.\doi{https://doi.org/10.1016/j.nucengdes.2018.07.005}{ DOI: 10.1016/j.nucengdes.2018.07.005}
\item \textbf{(2017) "A feature point identification method for positron emission particle tracking with multiple tracers". Nuclear Instruments and Methods in Physics Research Section A Accelerators Spectrometers Detectors and Associated Equipment. Indexada en SCOPUS - Instrumentation (Q1); Nuclear and High Energy Physics (Q2)}.\doi{https://doi.org/10.1016/j.nima.2016.10.057}{ DOI: 10.1016/j.nima.2016.10.057}
\item \textbf{(2017) "Three-dimensional spatiotemporal tracking of fluorine-18 radiolabeled yeast cells via positron emission particle tracking". Plos One. Indexada en SCOPUS - Agricultural and Biological Sciences (miscellaneous) (Q1); Biochemistry, Genetics and Molecular Biology (miscellaneous) (Q1); Medicine (miscellaneous) (Q1)}.\doi{https://doi.org/10.1371/journal.pone.0180503}{ DOI: 10.1371/journal.pone.0180503}
\item (2016) "Tracking synthetic particle paths generated in GATE with multi-positron emission particle tracking (MPEPT)". Transactions of the American Nuclear Society. \textbf{Conferencia Indexada en SCOPUS}. \underline{(Sin Filiación)}
\item \textbf{(2016) "A novel clustering approach to positron emission particle tracking". Nuclear Instruments and Methods in Physics Research Section A Accelerators Spectrometers Detectors and Associated Equipment. Indexada en SCOPUS - Instrumentation (Q1); Nuclear and High Energy Physics (Q2)}.\doi{https://doi.org/10.1016/j.nima.2015.11.136}{ DOI: 10.1016/j.nima.2015.11.136} \underline{(Sin Filiación)}









}


%%WEB OF SCIENCE
\newcommand{\numpublicacionesWos}{0 }
%% 6 Artículos, 1 Review, Artículos de Conferencia y 3 Capítulos de Libros
\newcommand{\distribucionArticulosWos}{1 Artículo y 5 Artículos de Conferencias }

\newcommand{\detalleWos}{
\item (2017) "THE LEARNING STYLE IN LOCAL HIGHER EDUCATION: EXPERIENTIAL MODEL AND CO-CREATION". INTED2017 Proceedings. \textbf{Conferencia Indexada en Conference Proceedings Citation Index (CPCI)}.
\item (2017) "APPROACHING OF ICT IN CO-CREATION OF DIGITAL EDUCATIONAL MATERIALS WITH SUPPORT OF AUTHOR'S TOOLS". EDULEARN17 Proceedings. \textbf{Conferencia Indexada en Conference Proceedings Citation Index (CPCI)}.
\item (2016) "DIGITAL DIVIDE ASSOCIATED WITH ADOPTION OF INFORMATION AND COMMUNICATION TECHNOLOGIES (ICTS) IN SMALL AND MEDIUM BUSINESSES (SMBS)". ICERI2016 Proceedings. \textbf{Conferencia Indexada en Conference Proceedings Citation Index (CPCI)}.
\item (2016) "INTERESTS AND NEEDS IN THE MONITORING FOR GRADUATES. A CASE STUDY". EDULEARN16 Proceedings. \textbf{Conferencia Indexada en Conference Proceedings Citation Index (CPCI)}.
\item (2016) "THE UNIVERSITY AND THE SOCIAL ENTREPRENEURSHIP". INTED2016 Proceedings. \textbf{Conferencia Indexada en Conference Proceedings Citation Index (CPCI)}.
}


%%REGIONALES
\newcommand{\numpublicacionesregionales}{0 }
\newcommand{\detalleRegionales}{
  \item (2024) "LIMITACIONES PARA LA APLICACIÓN DE TECNOLOGÍA SOCIAL EN LA PROTECCIÓN DEL PÁRAMO". Revista Estudios de la Gestión. \textbf{ Indexada en Scielo}. 
  
}

\newcommand{\aniosRegionales}{0 }


%%MEMORIAS
\newcommand{\numMemorias}{0 }
\newcommand{\aniosMemorias}{ }
\newcommand{\detalleMemorias}{
\item (2013) "Inclusive and beneficial? Governance in global food value chains in Costa Rica". 138th EAAE Seminar on Pro-poor Innovations in Food Supply Chains, Ghent Belgium. \textbf{ No se puede verificar la indexación}.
}


%%LIBROS Y CAP. LIBROS
\newcommand{\numLibros}{0 }
\newcommand{\detalleLibros}{
  \item (2017) "Ecuador". Challenges and Opportunities for Food and Nutrition Security for the Americas: The vision of the Academies of Sciences. \textbf{ Cap. Libro}.
}


%%Publicaciones 5 años de todo 2015-2019
\newcommand{\numpublicacionescincoaios}{555555555 }


\newcommand{\numTotalPubRegyScopus}{10 }